### 2025-03-08 download-football-data.qmd
20250308 - update citations

Data Dictionaries are metadata that describe the meaning of the variables in a dataset.
You can find Data Dictionaries for the various National Football League (NFL) datasets at the following link: <https://nflreadr.nflverse.com/articles/index.html>.

@@

This chapter extensively uses merging to process the data for later use.
See @sec-merging for a reminder of how to perform merging, the types of merges, and what you can expect when you merge data objects with different formats.
Guidance for how to merge the various NFL-related data files is provided at the following link: <https://github.com/nflverse/nfldata/blob/master/DATASETS.md>.

>>>>

Data Dictionaries are metadata that describe the meaning of the variables in a dataset.
@Ho2025 provide Data Dictionaries for the various National Football League (NFL) datasets at the following link: <https://nflreadr.nflverse.com/articles/index.html>.

@@

This chapter extensively uses merging to process the data for later use.
See @sec-merging for a reminder of how to perform merging, the types of merges, and what you can expect when you merge data objects with different formats.
Guidance for how to merge the various NFL-related data files is provided by @Sharpe2020: <https://github.com/nflverse/nfldata/blob/master/DATASETS.md>.

### 2025-03-08 fantasy-football.qmd
20241017 - fix width of image of field?
20241018 - figure sizing
20250308 - update citations

Football is the most widely watched sport in the United States.^[<https://news.gallup.com/poll/610046/football-retains-dominant-position-favorite-sport.aspx> (archived at <https://perma.cc/X2UG-RAAK>); <https://www.statista.com/statistics/1430289/most-watched-sports-leagues-usa/> (archived at <https://perma.cc/JNU6-S96A>)]

@@

Here is a video that provides a brief introduction to American football:

@@

::: {#fig-footballField}
![](images/footballField.png){width=50% fig-alt="A Diagram of a Football Field. The yard markers depict the distance from the nearest end zone. The orange shaded area is called the "red zone", where chances of scoring points are highest. The original figure was modified to depict field goal posts. (Figure retrieved from <https://commons.wikimedia.org/wiki/File:American_football_field.svg>"}

@@

Fantasy football is one of the most widely played games in the history of games.
It is estimated that around 62 million people play fantasy sports^[<https://thefsga.org/industry-demographics/> (archived at <https://perma.cc/9PB8-ZDJJ>)], of whom around 29 million play fantasy football.^[<https://www.statista.com/topics/10895/fantasy-sports-in-the-us/> (archived at <https://perma.cc/8YSN-UUNT>)]
As noted in the [Introduction](intro.qmd), fantasy football is an online game where participants assemble (i.e., "draft") imaginary teams composed of real-life National Football League (NFL) players.^[Fantasy leagues are also available for [baseball](https://en.wikipedia.org/wiki/Fantasy_baseball), [basketball](https://en.wikipedia.org/wiki/Fantasy_basketball), and many other sports.]
The participants are in charge of managing and making strategic decisions for their imaginary team to have the best possible team that will score the most points.
Thus, the participants are called "managers".
Managers make decisions such as selecting which players to draft, selecting which players to play (i.e., "start") on a weekly basis, identifying players to pick up from the remaining pool of available players (i.e., waiver wire), and making trades with other teams.

>>>>

Football is the most widely watched sport in the United States [archived at <https://perma.cc/X2UG-RAAK>; @Jones2024; archived at <https://perma.cc/JNU6-S96A>; @statistica2023].

@@

Here is a video that provides a brief introduction to American football [@Ly2015]:

@@

::: {#fig-footballField}
![](images/footballField.png){width=50% fig-alt="A Diagram of a Football Field. The yard markers depict the distance from the nearest end zone. The orange shaded area is called the 'red zone', where chances of scoring points are highest. The original figure was modified to depict field goal posts. (Figure retrieved from <https://commons.wikimedia.org/wiki/File:American_football_field.svg>)"}

@@

Fantasy football is one of the most widely played games in the history of games.
It is estimated that around 62 million people play fantasy sports [archived at <https://perma.cc/9PB8-ZDJJ>; @FSGA2023], of whom around 29 million play fantasy football [archived at <https://perma.cc/8YSN-UUNT>; @statistica2023a].
As noted in the [Introduction](intro.qmd), fantasy football is an online game where participants assemble (i.e., "draft") imaginary teams composed of real-life National Football League (NFL) players.^[Fantasy leagues are also available for [baseball](https://en.wikipedia.org/wiki/Fantasy_baseball), [basketball](https://en.wikipedia.org/wiki/Fantasy_basketball), and many other sports.]
The participants are in charge of managing and making strategic decisions for their imaginary team to have the best possible team that will score the most points.
Thus, the participants are called "managers".
Managers make decisions such as selecting which players to draft, selecting which players to play (i.e., "start") on a weekly basis, identifying players to pick up from the remaining pool of available players (i.e., waiver wire), and making trades with other teams.

### 2025-03-08 getting-started.qmd
20250308 - update citations

The following article provides additional resources and good guidance: <https://www.r-bloggers.com/where-to-get-help-with-your-r-question/> (archived at <https://perma.cc/4RRE-KL33>).

@@

- Read the posting guidelines before posting!
- Be respectful of other people and their time.
`R` is free software.
People are offering their free time to help.
They are under no obligation to help you.
If you are disrespectful or act like they owe you anything, you will rub people the wrong way and will be less likely to get help.
- Provide a minimal, reproducible example.
Providing a minimal, reproducible example can be crucial for getting a helpful response.
By going to the trouble of creating a minimal, reproducible example and identifying the minimum conditions necessary to reproduce the issue, you will often figure out how to resolve it.
Here are guidelines on providing a minimal, reproducible example: <https://stackoverflow.com/help/minimal-reproducible-example> (archived at <https://perma.cc/6NUB-UTYF>).
Here are a good example and guidelines for providing a minimal, reproducible example in `R`: <https://stackoverflow.com/a/5963610> (archived at <https://perma.cc/PC9L-DQZG>).
My strong recommendation is to provide a `reprex` whenever possible: <https://reprex.tidyverse.org>.
Here are Reprex do's and don'ts: <https://reprex.tidyverse.org/articles/reprex-dos-and-donts.html>.

>>>>

@Salmon2018 provides additional resources and good guidance for getting help with `R`: <https://masalmon.eu/2018/07/22/wheretogethelp/> (archived at <https://perma.cc/4RRE-KL33>).

@@

- Read the posting guidelines before posting!
- Be respectful of other people and their time.
`R` is free software.
People are offering their free time to help.
They are under no obligation to help you.
If you are disrespectful or act like they owe you anything, you will rub people the wrong way and will be less likely to get help.
- Provide a minimal, reproducible example.
Providing a minimal, reproducible example can be crucial for getting a helpful response.
By going to the trouble of creating a minimal, reproducible example and identifying the minimum conditions necessary to reproduce the issue, you will often figure out how to resolve it.
@StackOverflow2025 offers guidelines on providing a minimal, reproducible example: <https://stackoverflow.com/help/minimal-reproducible-example> (archived at <https://perma.cc/6NUB-UTYF>).
@StackOverflow2018 offers a good example and guidelines for providing a minimal, reproducible example in `R`: <https://stackoverflow.com/a/5963610> (archived at <https://perma.cc/PC9L-DQZG>).
My strong recommendation is to provide a `reprex` whenever possible: <https://reprex.tidyverse.org>.
@Bryan2025 provide Reprex do's and don'ts: <https://reprex.tidyverse.org/articles/reprex-dos-and-donts.html>.

### 2025-03-08 index.qmd
20250308 - update citations

I strive to follow [principles of accessibility](https://bookdown.org/yihui/rmarkdown-cookbook/html-accessibility.html) (archived at <https://perma.cc/8XJ9-Q6QJ>) to make the book content accessible to people with visual impairments and physical disabilities.
If there are additional ways I can make the content more accessible, please let me know.

>>>>

I strive to follow [principles of accessibility](https://bookdown.org/yihui/rmarkdown-cookbook/html-accessibility.html) [archived at <https://perma.cc/8XJ9-Q6QJ>; @Xie2024; @Xie2020_packages] to make the book content accessible to people with visual impairments and physical disabilities.
If there are additional ways I can make the content more accessible, please let me know.
